---
title: "Stat 123 Homework 15"
author: "Tyler Hatchett"
date: "10/14/19"
output: word_document
---

Data on the daily concentration of fine particles pollutant (PM2.5) for all
monitor sites in Utah County is available in .csv files attached to the assignment, 
with each file having data from a year. These files have the name format
"ad_viz_plotval_data-XXXX.csv" (where XXXX is place holder for the year).  

Write a function named 'air' that
takes a 'year' argument and returns a data.frame containing that data for
that year, suppressing the automatic conversion to factors.
```{r}
air <- function(x){
  air09 <- read.csv(file = "/Users/Tyler Hatchett/Downloads/ad_viz_plotval_data-2009.csv", header = TRUE, stringsAsFactors = FALSE)
  air10 <- read.csv(file = "/Users/Tyler Hatchett/Downloads/ad_viz_plotval_data-2010.csv", header = TRUE, stringsAsFactors = FALSE)
  air11 <- read.csv(file = "/Users/Tyler Hatchett/Downloads/ad_viz_plotval_data-2011.csv", header = TRUE, stringsAsFactors = FALSE)
  air12 <- read.csv(file = "/Users/Tyler Hatchett/Downloads/ad_viz_plotval_data-2012.csv", header = TRUE, stringsAsFactors = FALSE)
  air13 <- read.csv(file = "/Users/Tyler Hatchett/Downloads/ad_viz_plotval_data-2013.csv", header = TRUE, stringsAsFactors = FALSE)
  air14 <- read.csv(file = "/Users/Tyler Hatchett/Downloads/ad_viz_plotval_data-2014.csv", header = TRUE, stringsAsFactors = FALSE)
  air15 <- read.csv(file = "/Users/Tyler Hatchett/Downloads/ad_viz_plotval_data-2015.csv", header = TRUE, stringsAsFactors = FALSE)
  air16 <- read.csv(file = "/Users/Tyler Hatchett/Downloads/ad_viz_plotval_data-2016.csv", header = TRUE, stringsAsFactors = FALSE)
  
 return(list(air09, air10, air11, air12, air13, air14, air15, air16)) 
  
}
```

Using lapply, make a list containing a data.frame for each year.
```{r}
airpollution <- air(x)
```

Combine all the data.frames in the list to one data.frame (without losing any data).
```{r}
combinedair <- rbind(airpollution[[1]], airpollution[[2]], airpollution[[3]], airpollution[[4]], airpollution[[5]], airpollution[[6]], airpollution[[7]], airpollution[[8]])
```


Summarize this big data.frame to yield a data.frame containing only the
average "DAILY_AQI_VALUE" and the average "Daily.Mean.PM2.5.Concentration" for each
value of "Date".
```{r}
library(plyr)

avg.by.date <- ddply(combinedair, .(Date), summarize, meanAQI = mean(DAILY_AQI_VALUE), meanpm2.5 = mean(Daily.Mean.PM2.5.Concentration))
```

Produce a scatter plot of the average "Daily.Mean.PM2.5.Concentration" (on
the y-axis) and average "DAILY_AQI_VALUE" (on the x-axis).
```{r}
attach(avg.by.date)
plot(avg.by.date$meanAQI, avg.by.date$meanpm2.5, main = "Scatter plot for Air Pollution", xlab = "Daily AQI Value", ylab = "Daily Mean Pm2.5 Concentration")
```

Add vertical lines at 50, 100, and 150 on the x-axis.  Hint: See the help for
the "abline" function.
```{r}
plot(avg.by.date$meanAQI, avg.by.date$meanpm2.5, main = "Scatter plot for Air Pollution", xlab = "Daily AQI Value", ylab = "Daily Mean Pm2.5 Concentration")

abline(v=50)
abline(v=100)
abline(v=150)
```

