---
title: "Homework 13"
author: "Tyler Hatchett"
date: "10/8/2019"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Complete the definition of the function.  It takes one argument "year" (where
"year" can range from "1910" to "2013") and returns a data.frame giving the
count by gender of names for babies born in the specified year.  The variable
names should be "name", "sex", and "count".  If the value of the "year"
argument is "all", a data.frame containing all the data should be returned.
Use the data provided in the attached folder "names-full-datasets"  Hint: You will probably want to use the 'paste' function.
```{r}
#reading in the data.
baby.names <- function(year="all"){
  setwd("/Users/Tyler Hatchett/Downloads/names-full-datasets/names-full-datasets")
  if(year== "all"){
    fulldata <- data.frame()
    for (i in 1910:2013){
      filename <- paste("yob", i, ".txt", sep= "")
      data <- read.table(filename, sep= ",", stringsAsFactors = FALSE, col.names = c("Name", "Sex", "Count"))
      data$Year <- i
      fulldata <- rbind(fulldata, data)
    }
    return(fulldata)
  } else{
    fulldata <- data.frame()
      for(c in year){
        filename <- paste("yob", c, ".txt", sep = "")
        data <- read.table(filename,sep= ",", stringsAsFactors = FALSE, col.names = c("Name", "Sex", "Count"))
        dataYear <- c
        fulldata <- rbind(fulldata, data)
      }
    return(fulldata)
  }
}  
  
  
```

Execute the code below and use the resulting data.frame for the rest of this problem.

```{r}
yall <- baby.names() 

```

Complete the function definition below that counts the
number of occurences of the supplied "name" for a vector of "years".

```{r}
library(plyr)
library(dplyr)

lookup <- function(name,years)  {
  count_by_year <- yall %>% filter(Name == name) %>% group_by(Year) %>% filter(Year %in% seq(1913,2013, by = 10)) %>%  summarize(Total=sum(Count))
return(count_by_year)
}                             

```


Use your function to find how many babies where born with the name "Jennifer"
in each of the following years: 1913, 1923, ..., 2003, 2013.
```{r}
lookup("Jennifer", 1913:2013)      

```


What is the overall most popular name for a boy?  How about for a girl?
```{r}
yall%>%filter(Sex == "M")%>%group_by(Name) %>%summarize(Total = sum(Count))%>% arrange(desc(Total)) %>%head(1)
#James is the most popular name for a boy.
yall%>%filter(Sex == "F")%>%group_by(Name) %>%summarize(Total = sum(Count))%>% arrange(desc(Total)) %>%head(1)
#Mary is the most popular name for a girl.

```

Produce a line plot showing the proportion of babies named "Mary" among
all female names over time.
```{r}
marycount <- yall%>% group_by(Year) %>% filter(Name == "Mary") %>% filter(Sex == "F")%>% select(Count, Year)
popfem <- yall %>% group_by(Year) %>% filter(Sex == "F")%>% summarise(Total = sum(Count))

maryprop <- merge(marycount, popfem, by.x = "Year", by.y = "Year")
head(maryprop)

final <- maryprop %>% mutate(Prop = Count/Total)

library(ggplot2)
ggplot(final) + geom_line(aes(x=Year, y= Prop))

```